---
title: "rainbbow"
author: "ciro barone"
date: "Thursday, July 10, 2014"
output: html_document
runtime: shiny

tutorial: http://rmarkdown.rstudio.com/authoring_shiny.html?version=0.98.939&mode=desktop
---


```{r, echo=FALSE}

shinyUI(pageWithSidebar( 
  headerPanel("test"),

  sidebarPanel(h4("Controls"),
               dateRangeInput("Range Date", "Range Date:",
               start = "201309",
               end   = "201312"),
               
               selectInput("var1", "Segmenta per:",
            c("Festivo" = "Festivo",
              "Lavorativo" = "Lavorativo")),
            
            checkboxGroupInput("var2", "Seleziona categoria:",
                   c("Farmacie" = "farmacie",
                     "Ristoranti" = "ristoranti",
                     "Gommisti" = "gommisti"))         
               
               )
  ))

mainPanel()




```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package="shiny"),
  options=list(
    width="100%", height=550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



